ESRC SDAI Application

### 2019-06-12 case_for_support.tex
Wednesday

\section{Aims}

\subsection{Who does not report DA?}

The WMP data are cases that have been reported to the police. The CSEW allows an estimate of the prevalence of domestic abuse. The discrepancy between the two datasets allows us to estimate the reporting gap. We first explore the characteristics of offenders and victims.

While the CSEW provides us with accurate information on the characteristics of victims, it does not contain information on the perpetrators. Combining the two datasets helps us find commonalities between the perpetrators of abuse cases that are

@@

Aim 1: Who perpetrates? Who becomes a victim? victim/perpetrator characteristics (gender/ethnicity); deprivation and domestic abuse? Find out what kind of cases get reported. Break down the 17\% based on socioeconomic and incident characteristics.

\subsubsection{A description of victims and perpetrators}

victim future behavs, risk factors, intervention possibility

@@

\subsubsection{Association with other criminal behaviours}

Increasing victim's willingness to report domestic abuse is key in reducing prevalence and preventing escalation that can potentially result in domestic homicide. We will use the CSEW to understand the demographic and socioeconomic predictors of the decision to report the abuse to the police, and identify specific groups who are less likely to report. We can contrast and validate these findings using the crime dataset.

\subsection{Predicting serious harm}

For example, incidents involving drugs or alcohol intoxication: some individuals may end up in an abusive relationship because of an existing dependency, or a dependency may develop as a counterproductive strategy of coping with the abusive relationship.

\subsection{Collateral damage}
It also contains information about  multiple members of the household. This allows us to examine whether young individuals living in a household with a victim of domestic abuse are more likely to be victims or perpetrators of other types of crime. By using other questions in the CSEW, we can also measure whether these children are more likely to perpetrate crimes, and to be involved in gang related activities.

@@

\subsection{The Temporal Course and the Decision to Report}

The crime dataset will further allow us to follow victim-offender pairs over time, and explore how the severity and nature of reported abuse changes over time. We will also be able to identify high-risk days of the year (e.g., birthdays, Christmas, Halloween) by the characteristics of the victim-offender pair and the pattern and duration of abuse. Insights from these analyses can inform decisions about the optimal timing and target audience for domestic abuse awareness campaigns.

>>>>

\section*{Research Programme}

In outlining the research program we specify X core regression analyses, which we will preregister ahead of beigging research on the OSF. These will be complemented with the robustness checks and further exploratory regressions (see, Trendl Football, for an example of this approach).

\subsection*{1. Who is abused and who reports abuse?}

Aim: Who perpetrates? Who is a victim? victim/perpetrator characteristics (gender/ethnicity); Find out what kind of cases get reported. Break down the 17\% based on socioeconomic and incident characteristics.

In our first programme we will answer the question ``Who doesn't report domestic abuse?''. Increasing victim's willingness to report domestic abuse is key in reducing prevalence and preventing escalation that can potentially result in domestic homicide. We will also provide more broad demographic descriptions of the victims and the perpetrators of domestic abuse.

We will use the CSEW to understand the demographic and socioeconomic predictors of the decision to report the abuse to the police, and identify specific groups who are less likely to report. We are able to do this because CSEW respondents indicated whether they reported the abuse to the police  and whether the police came to know of the abuse in another way (Question X).

Regression 1: data --- subset of people who in CSEW responding that they have been abused

	unreported abuse / reported abuse ~ 
	[demographics] age + sex + marital status + earnings + ... 
	other crime dummies + ...
	[information about abuse] level of harm + ...
	[geomatched stuff] socioeconomic status

Respondents also answered questions indicating the level of harm that they have suffered, which will allow us to estimate how reporting and police awareness depend upon the level of harm. \NS{Anna: broaden this paragraph to be about all of the covariates}

Linear probability model (and logit model?)

We can contrast and validate these findings using the WMP dataset. 
The WMP data are cases that have been reported to the police. The CSEW data allow an estimate of the true underlying prevalence of domestic abuse. The discrepancy between the two datasets allows us to estimate the reporting gap. 
That is, we can use the WMP dataset to provide a second estimate of the degree of underreporting, indpendent of the CSEW respondent's indications of report. Discrepancy between reporting prevelence estimated from CSEW and the number of cases in the WMP data give important information about the police's recording and categorisation of domestic abuse cases---do police flag all of the cases of domestic abuse?  https://www.bbc.co.uk/news/uk-england-46867657

While the CSEW provides us with accurate information on the characteristics of victims, it does not contain information on the perpetrators. Combining the two datasets helps us find commonalities between the perpetrators of abuse cases that are.

We will also extend the analysis to provide a more general description of the victims of abuse by considering

Domestic abuse doesn't discriminate---well we can estimate this by comparing the 7.7\% for females and 4.4\% for males in the past year with the size of the coefficients.

Regression 2: 
	no abuse / abuse ~ 	[demographics] age + sex + marital status + earnings + employment + ... other crime dummies
		health + mental health +

\subsection{The time course of abuse and the predicting serious harm}

Aim:

The CSEW respondents indicated the level of harm, and we can use the CSEW to estimate the cross-sectional association between the most serious harm and other comorbid factors like alcohol, other crimes,

Regression 3: type of abuse ~ 
	visit hospital ~ 
	mental health ~

But cross-sectional data present a particular problem for making casual claims: For example, incidents involving drugs or alcohol intoxication: some individuals may end up in an abusive relationship because of an existing dependency, or a dependency may develop as a counterproductive strategy of coping with the abusive relationship.

The WMP dataset will further allow us to follow victim-offender pairs over time, and explore how the severity and nature of reported abuse changes over time. 
In the WMP data we can follow X victim-perp pairs for X years, with each pair appearing X times on average in the data.

We will also be able to identify high-risk days of the year (e.g., birthdays, Christmas, Halloween) by the characteristics of the victim-offender pair and the pattern and duration of abuse. Insights from these analyses can inform decisions about the optimal timing and target audience for domestic abuse awareness campaigns.

Regression 4: offense classification[proxy for harm] ~ .
	type of abuse ~ .

Future victim behaviours. Future perpetrator behaviours

serious event at t ~ stuff at t-1  + perpetrator previous crimes
 and 	a model with pair fixed effects

Murders are very rare, so we are adopting a ``near miss'' airline / nuclear industry strategy of predicting the more prevalent but less serious incidents.

Say pair fixed effects control for all non-time varying characteristics. With and without pair fixed effects let's use see how much state vs trait matters for prediction.

\subsection{Collateral damage}

Aim:

CSEW regression: child gang membership ~ any domestic abuse or reported DA [2x2 table of abuse/no abuse by gang / no gang]
Also estimate, given gang membership what fraction are DA---which links ot WMP analysis below

It also contains information about  multiple members of the household. This allows us to examine whether young individuals living in a household with a victim of domestic abuse are more likely to be victims or perpetrators of other types of crime. By using other questions in the CSEW, we can also measure whether these children are more likely to perpetrate crimes, and to be involved in gang related activities.

Match on name, location, and date of birth in WMP data to see effect on children

WMP regression:

take every juvinile in a gang and try to match all to domestic abuse cases----estimates of what fraction of gang members have co-morbid domestic abuse

What fraction of reported child abuse has comorbid DA; what fraction of DA has comorbid child abuse

Using school census we can go futher and estimate frequencies in a 2x2 child abuse  by domestic abuse table---providing we can match children to mothers.

Aim:

CSEW analysis

Unit of analysis is large geographical area in a year 
Time span 2005-

DA or not ~

Given DA: report or not ~

Fixed effects for region and year

WMP analysis

Unit of analysis is LSOA (MSOA?) per month or per quarter
Time span - 2010-2020

Number of DA cases ~

@@

Extend regression model X to include region fixed effects?

@@

@@

Mention we can construct some of these variables by access to "a very large UK bank" which whom we have a data sharing agreement. We cna build them from the row-per-transactino data for spending on current account and credit cards.
